%-------------------------
% Resume in LaTeX
% Author : Md Jobaer Islam Alif
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Md Jobaer Islam Alif} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+8801960024750}{+8801960024750}
    $|$
    \faAt \hspace{.5pt} \href{mailto:alifjobaer12@gmail.com}{alifjobaer12@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/alifjobaer12}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/alifjobaer12}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} Portfolio: \href{https://alifjobaer12.github.io}{Website}
    $|$
    \faMapMarker \hspace{.5pt} h12, r11, PC Culture Housing Society, Adabor, Dhaka 1207
\end{center}

%----------- EDUCATION -----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {Bangladesh University of Business and Technology (BUBT)}{Dhaka, Bangladesh}
      {Undergraduate in Computer Science and Engineering}{Expected 2027}
      {}{}
    \resumeEducationHeading
      {Doweed Public School and College}{Jessore, Bangladesh}
      {Higher Secondary Certificate (HSC)}{Completed 2022}
      {}{}
    \resumeEducationHeading
      {Jessore Shikkha Bord Gov. Model School And College}{Jessore, Bangladesh}
      {Secondary School Certificate (SSC)}{Completed 2020}
      {}{}
  \resumeSubHeadingListEnd

%----------- SKILLS -----------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeItemListStart
        \resumeItem{\textbf{Programming Languages:} C, C++, Python, Java, JavaScript, HTML, CSS, etc.}
        \resumeItem{\textbf{Frameworks \& Tools:} React.js, Tailwind CSS, MySQL, Git, CustomTkinter, etc.}
        \resumeItem{\textbf{Specializations:} Competitive Programming, Problem Solving, Data Structures \& Algorithms.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- PROJECTS -----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Productivity Tracker} | \href{https://github.com/alifjobaer12/project-productivity-tracker-}{GitHub}}{}
\resumeItemListStart
    \resumeItem{A desktop productivity management application to track tasks, deadlines, and progress using C/C++ for robust performance and minimal memory usage.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Assignments } | \href{https://github.com/alifjobaer12/Assignment-1}{GitHub}}{}
\resumeItemListStart
    \resumeItem{Web development assessment project demonstrating HTML, CSS, and JavaScript skills. Live demo available \href{https://alifjobaer12-1stassignment.surge.sh/}{here}.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Assignments  (Portfolio)} | \href{https://github.com/alifjobaer12/My-Portfolio}{GitHub}}{}
\resumeItemListStart
    \resumeItem{Portfolio web application created as part of a web development assessment. Showcases projects, skills, and personal branding. Live demo: \href{http://alifjobaer12.me/}{here}.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{School Management System} | \href{https://github.com/alifjobaer12/School_Management_System}{GitHub}}{}
\resumeItemListStart
    \resumeItem{Desktop application for managing student data, attendance, and subjects using Python, CustomTkinter, and MySQL.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ChronoMate} | \href{https://github.com/alifjobaer12/ChronoMate}{GitHub}}{}
\resumeItemListStart
    \resumeItem{Python-based desktop time management application utilizing CustomTkinter and MySQL for data handling.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{YouTube Downloader} | \href{https://github.com/alifjobaer12/YoutubeDownloader}{GitHub}}{}
\resumeItemListStart
    \resumeItem{Python desktop application built with CustomTkinter to download videos and audio from YouTube efficiently.}
\resumeItemListEnd


%----------- EXPERIENCE -----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeItem{To be added after graduation.}
\resumeSubHeadingListEnd

%----------- ACHIEVEMENTS -----------
\section{Achievements}
\resumeSubHeadingListStart
    \resumeItem{You can add your future achievements here.}
\resumeSubHeadingListEnd

%----------- CONTACT & SOCIAL LINKS -----------
\section{Contact \& Social Links}
\resumeSubHeadingListStart
    \resumeItem{\textbf{Email:} alifjobaer12@gmail.com}
    \resumeItem{\textbf{Phone:} +8801960024750}
    \resumeItem{\textbf{Location:} h12, r11, PC Culture Housing Society, Adabor, Dhaka 1207}
    \resumeItem{\textbf{LinkedIn:} \href{https://www.linkedin.com/in/alifjobaer12}{link}}
    \resumeItem{\textbf{GitHub:} \href{https://github.com/alifjobaer12}{link}}
    \resumeItem{\textbf{Twitter:} \href{https://x.com/allifjobaer12}{link}}
    \resumeItem{\textbf{Codeforces:} \href{https://codeforces.com/profile/alifjobaer12}{link}}
    \resumeItem{\textbf{Facebook:} \href{https://www.facebook.com/jobaer.alif.3}{link}}
    \resumeItem{\textbf{Instagram:} \href{https://www.instagram.com/j.i.alif_}{link}}
\resumeSubHeadingListEnd

\end{document}
